---
title: "Vignette_mobiCD"
output: rmarkdown::html_vignette
vignette: >
  %\VignetteIndexEntry{Vignette_mobiCD}
  %\VignetteEngine{knitr::rmarkdown}
  %\VignetteEncoding{UTF-8}
---

```{r, include = FALSE}
knitr::opts_chunk$set(
  collapse = TRUE,
  comment = "#>"
)
```

```{r setup}
library(mobiCD)
```

# Description

# Individual function explanation

## generate_dna()

The first function called generate_dna

## match_replace()

## split_into_codons(sequence)

split_into_codons() takes a sequence and splits it into codons (sequences of 3). It can take any sequence, but to work with the other functions in the package an RNA sequence should be used.

```{r}
split_into_codons("AUGUUUUAA")
```

If the length of the sequence is not divisible by 3 the excess bases are not included

```{r}
split_into_codons("AUGUUUUAAGG")
```

Another starting point for the splitting can be chosen. The bases before that point in the sequence are not included

```{r}
split_into_codons("AUGUUUUAAGG",
                  start = 3)
```

## tRNA_rep()

## plot_content()

# Example of package usage
