---
title: "Vignette_mobiCD"
output: rmarkdown::html_vignette
vignette: >
  %\VignetteIndexEntry{Vignette_mobiCD}
  %\VignetteEngine{knitr::rmarkdown}
  %\VignetteEncoding{UTF-8}
---

```{r, include = FALSE}
knitr::opts_chunk$set(
  collapse = TRUE,
  comment = "#>"
)
```

```{r setup}
library(mobiCD)
```

# Description

The whole package allows us to follow the central dogma of molecular biology. It generates the flow of genetic information from DNA to RNA to protein, a process involving transcription (DNA to RNA) and translation (RNA to protein). Each of the unique codons are translated into different amino acids and predictions of different protein properties can be made acording to the different amino acid quantities in a sequence.

# Individual function explanation

## generate_dna(length)

The first function called generate_dna() is used for creating a random DNA sequence that contains four nucleotides: "A", "T", "C", "G". Inside the function a wanted length of the sequence is entered and DNA is generated randomly into a single string. An example of a 10 nucleotide having sequence can be seen below.

```{r}
generate_dna(10)
```

## match_replace()

## split_into_codons()

## tRNA_rep()

## plot_content()

# Example of package usage
